---
title: "Segmentation Code Overview"
subtitle: "nwasc r-package"
author: "Rob Fowler, U.S. Fish and Wildlife Service"
email: "robert_fowler@fws.gov"
date: "03 OCT 2018"
output: slidy_presentation
---


## Guiding Principles

- Simple
- Reproducible results
- Well documented

## R-Package Solution

* Organized code 
* Documentation standards
    + The Comprehensive R Archive Network (CRAN) https://cran.r-project.org
    + RStudio  https://rstudio.com
    + Tidyverse https://www.tidyverse.org
* Testable style requirements
* Facilitates unit testing
* Works well with GitHub https://www.github.com

## Package Location and Installing

* https://github.com/robgf/nwasc
* Install:

```{r echo=TRUE, eval=FALSE}
devtools::install_github("robgf/nwasc")
```

## Organized Code

* Keeping it simple ~883 files in 326 folders 
* Four (4) exported functions
    + All with prefix "nwasc_"
    + Two Segmentation Functions
        - CTS data: nwasc_segmentCTS()
        - DTS data: nwasc_segmentDTS()
    + Two function for finalizing results into one file
* Example of clean data (circa Spring 2017) included in package (35MB)

## Documentation

* R/Tidyverse has two documentation forms, short and long
* Short form
    + Technical internal documentation
    + Allows for standard R help:
```{r echo=TRUE, eval=FALSE}
?nwasc
?nwasc_SegmentCTS
```
* Long form vignette
    + Full example of running code


## Running code

* Requirements for catalog query in documentation
    + Webpage
    + Vignette
    + Function documentation

* Due to the size of the NWASC this takes a while
    
```{r echo=TRUE, eval=FALSE}
library(nwasc)
seg.dat.phase2 = nwasc_segmentCTS(nwasc.ph2.obs.pre,
                            nwasc.ph2.shp.pre,
                            nwasc.ph2.cts.dat,

seg.dat.phase1.cts = nwasc_segmentCTS(nwasc.ph1.obs.pre,
                                nwasc.ph1.shp.pre,
                                nwasc.ph1.cts.dat,

seg.dat.phase1.dts = nwasc_segmentDTS(nwasc.ph1.dts.obs.dat,
                                nwasc.ph1.dts.dat)

segmented_seabird_catalogs <- nwasc_bind_phases(seg.dat.phase2, seg.dat.phase1.cts, seg.dat.phase1.dts)
nwasc_write_segmented_csv(segmented_seabird_catalogs)
zip("segmented_results", file = "segmented_seabird_catalog-2018-09-27-combined_transects_3 .csv")

```

## Testing

* Testing inputs
    +Occurs with QA/QC of Catalog
* Testing functions
    + unit tests of functions
    + presently at 89% coverage
        - .onLoad can't be tested externally
        - Legacy code has unused options
        - Writing final output produces >200MB file and
          shouldn't be tested on third party server



## Passed Standards

* External Continuous Integration Services
    + Travis CI [![Travis build status](https://travis-ci.org/robgf/nwasc.svg?branch=master)](https://travis-ci.org/robgf/nwasc)
    + AppVeyor [![Travis build status](https://travis-ci.org/robgf/nwasc.svg?branch=master)](https://travis-ci.org/robgf/nwasc)
    
* Test Coverage Reviews
    + Codecov [![Codecov test coverage](https://codecov.io/gh/robgf/nwasc/branch/master/graph/badge.svg)](https://codecov.io/gh/robgf/nwasc?branch=master)
    + Coveralls [![Coveralls test coverage](https://coveralls.io/repos/github/robgf/nwasc/badge.svg)](https://coveralls.io/r/robgf/nwasc?branch=master)

## Viewing Results (ongoing work)

* Leaflet Map of tracks with observations
* Overlay of segments
* Example: 
    + Different discretization for subset of NWASC
    + Winter seaducks FWS flights 'segments' common bins over years
* Next Steps:
    + Implement shiny version of maps for catalog
    + Similar to ARCGIS/QGIS maps, but without software or knowledge 

* Move copy of repository to FWS GitHub account
    
    
