---
title: Location
---
```{r, child ="_header.rmd"}
```
## Location
Conference Room A

National Wildlife Visitors' Center

10901 Scarlet Tangier Loop, Laurel, MD 20708



## Directions

<!--html_preserve-->
<div class="mapouter"><div class="gmap_canvas"><iframe width="600" height="500" id="gmap_canvas" src="https://maps.google.com/maps?q=10901%20Scarlet%20Tangier%20Loop%2C%20Laurel%2C%20MD%2020708&t=&z=11&ie=UTF8&iwloc=&output=embed" frameborder="0" scrolling="no" marginheight="0" marginwidth="0"></iframe><a href="https://www.embedgooglemap.net"></a></div><style>.mapouter{text-align:right;height:500px;width:600px;}.gmap_canvas {overflow:hidden;background:none!important;height:500px;width:600px;}</style></div>
<!--/html_preserve-->

## Site Information

Wi-fi should be up and going. Thanks to USPS Patuxent (Derek, Eddie, et. al.)

Site is a pack out facility and food/drink is not permitted in lobby. Please be respectful to the volunteers that will be working there on the weekend.

Link to menu?  Description.

## Date and Time
* Date: Saturday 11 August 2018
* Time: 9:30 am to 4:00 pm


Planning midmorning start winding up early evening. Feel free to come and go as you want. 

## Event day contacts


```{r, child ="_footer.rmd"}
```
